---
title: "Benefit description"
output: 
  html_document:
    theme: united
    toc: TRUE
    toc_float: TRUE
params:
  BENEFIT_BIRTHCOHORTS_CALENDARTIME: NULL
  BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION: NULL
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r parameters, include=FALSE}
BENEFIT_BIRTHCOHORTS_CALENDARTIME = params$BENEFIT_BIRTHCOHORTS_CALENDARTIME
BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION = params$BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION
```

This is the description of **BENEFIT_BIRTHCOHORTS_CALENDARTIME** and  **BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION** datasets.
<br>
This file contains graphical tools and tables to summarize the benefits data obtained from the script regarding a specific cohort. 
<br>
```{r plot preparation, include=FALSE}
if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2 )

if (!require("ggthemes")) install.packages("ggthemes")
library(ggthemes )

if (!require("lubridate")) install.packages("lubridate")
library(lubridate )

```
#  BENEFIT_BIRTHCOHORTS_CALENDARTIME

<br>
The graph and table below show the IR for each weeks (in calendar time), regarding the cohort with the following characteristics:

- birth_cohort = "all_birth_cohorts" 
- vx_manufacturer = "Pfizer"
- COVID = "L1"

<br>

## Graph

<br>
```{r plot1, include=TRUE}
######  BENEFIT_BIRTHCOHORTS_CALENDARTIME
######  birth_cohort == "all_birth_cohorts" & vx_manufacturer == "Pfizer"  & COVID == "COVID"
######  dose 1 vs dose 2
BENEFIT_BIRTHCOHORTS_CALENDARTIME_4plt <- BENEFIT_BIRTHCOHORTS_CALENDARTIME[birth_cohort == "all_birth_cohorts" & vx_manufacturer == "Pfizer"  & COVID == "L1"]
BENEFIT_BIRTHCOHORTS_CALENDARTIME_4plt <- BENEFIT_BIRTHCOHORTS_CALENDARTIME[, week:= ymd(week)]


BENEFIT_BIRTHCOHORTS_CALENDARTIME_plt <- ggplot(BENEFIT_BIRTHCOHORTS_CALENDARTIME_4plt, aes(x=week, y=IR, fill = dose)) + 
                                            geom_col(position=position_dodge( 5, preserve = "single"), alpha=0.5) +
                                            geom_errorbar(position=position_dodge( 5, preserve = "single"), aes(ymin=lb, ymax=ub, col=dose), width=.25) +
                                            labs(title = "Benefit: Calendar Time")+
                                            theme_hc()
BENEFIT_BIRTHCOHORTS_CALENDARTIME_plt
cat("\n")
cat("\n")

```
<br>

## Table

<br>

```{r table1, include=TRUE}
paged_table(BENEFIT_BIRTHCOHORTS_CALENDARTIME_4plt[order(week), .(week, IR)])
```
<br>

# BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION

<br>

The graph and table below show the IR for each weeks (numbers of weeks since vaccination), regarding the cohort with the following characteristics:

- birth_cohort = "all_birth_cohorts" 
- vx_manufacturer = "Pfizer"
- COVID = "L1"

<br>

## Graph

<br>
```{r plot2, include=TRUE}
BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION_4plot <- BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION[birth_cohort == "all_birth_cohorts" & vx_manufacturer == "Pfizer"  & COVID == "L1"]

BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION_plot <- ggplot(BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION_4plot, aes(x=week_since_vaccination, y=IR)) + 
                                                      geom_col(alpha=0.5, fill="salmon") +
                                                      geom_errorbar(position=position_dodge( 5, preserve = "single"), aes(ymin=lb, ymax=ub), width=.25, col="salmon") +
                                                      facet_grid( ~ dose)+
                                                      labs(title = "Benefit: Weeks since Vaccination")+
                                                      theme_hc()
                                                    
BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION_plot
cat("\n")
cat("\n")
```
<br>

## Table

<br>
```{r table2, include=TRUE}
paged_table(BENEFIT_BIRTHCOHORTS_TIMESINCEVACCINATION_4plot[order(week_since_vaccination), .(week_since_vaccination, dose, IR)])
```