---
title: "COVERAGE_BIRTHCOHORTS"
output: 
  html_document:
    theme: united
    toc: TRUE
    toc_float: TRUE
params:
  Dataset: NULL
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r parameters, include=FALSE}
  Dataset = params$Dataset
```

This is the description of **COVERAGE_BIRTHCOHORTS** dataset.
<br>
This file contains graphical tools and tables to summarize the vaccine coverage data obtained from the script. 

```{r plot preparation, include=FALSE}
if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2 )

if (!require("ggthemes")) install.packages("ggthemes")
library(ggthemes )

if (!require("lubridate")) install.packages("lubridate")
library(lubridate )

Dataset$week=ymd(Dataset$week)
#study_end <- as.Date(as.character(CDM_SOURCE[1,"recommended_end_date"]), date_format)
study_start <- as.Date("2020-11-30")

```

## Coverage

This section includes a graph showing the percentage of vaccine coverage by week. 
The data are also shown in the subsequent table. 

```{r plot1, include=TRUE}
t2<-Dataset[percentage != 0 & !is.na(percentage), sum(percentage), by= week]
setnames(t2, "V1", "percentage")


 p2 <- ggplot(t2, aes(week, percentage)) +   
         geom_col( alpha = 0.9, fill ="salmon", na.rm=TRUE)+
         scale_x_date(limit= c(study_start, study_end))

p2
rmarkdown::paged_table(t2)
```

## Coverage by manufacturer

This section includes a graph showing the percentage of vaccine coverage by week, divided by manifacturer. 
The data are also shown in the subsequent table. 

```{r plot2, include=TRUE}
t1<-Dataset[percentage != 0 & !is.na(percentage), sum(percentage), by= .(week, vx_manufacturer)]
setnames(t1, "V1", "percentage")
p1<-  ggplot(t1, aes(week, percentage, fill=vx_manufacturer)) +   
       geom_col(position = "dodge", alpha = 0.9, na.rm=TRUE)+
       scale_x_date(limit= c(study_start, study_end))

p1

rmarkdown::paged_table(t1)
```


## Coverage by dose

This section includes a graph showing the percentage of vaccine coverage by week, divided by dose number. 
The data are also shown in the subsequent table.

```{r plot4, include=TRUE}

t4<-Dataset[percentage != 0 & !is.na(percentage), sum(percentage), by= .(week, dose)]

setnames(t4, "V1", "percentage")

 p4 <- ggplot(t4, aes(week, percentage)) +   
        geom_col(alpha = 0.9, fill ="salmon", na.rm=TRUE)+
        scale_x_date(limit= c(study_start, study_end))+
        facet_grid(rows = vars(dose)) 

p4

rmarkdown::paged_table(t4)

```

## Coverage by dose and by manufacturer

This section includes a graph showing the percentage of vaccine coverage by week, divided by manifacturer and by dose number. 
The data are also shown in the subsequent table.
```{r plot3, include=TRUE}
 
t3<-Dataset[percentage != 0 & !is.na(percentage), sum(percentage), by= .(week, vx_manufacturer, dose)]

setnames(t3, "V1", "percentage")

 p3 <- ggplot(t3, aes(week, percentage, fill=vx_manufacturer)) +   
         geom_col(position = "dodge", alpha = 0.9, na.rm=TRUE)+
         scale_x_date(limit= c(study_start, study_end))+
         facet_grid(rows = vars(dose))

p3
rmarkdown::paged_table(t3)
```
