---
title: "DOSES_BIRTHCOHORTS"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r parameters, include=FALSE}
  Dataset = DOSES_BIRTHCOHORTS
```

This is the description of **DOSES_BIRTHCOHORTS** dataset.
<br>
This file contains graphical tools and tables to summarize the number of vaccines administered data obtained from the script. 

```{r plot preparation, include=FALSE}
if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2 )

if (!require("ggthemes")) install.packages("ggthemes")
library(ggthemes )

if (!require("lubridate")) install.packages("lubridate")
library(lubridate )

Dataset$week=ymd(Dataset$week)
Dataset=Dataset[birth_cohort=="all_birth_cohorts"]

# study_end <- as.Date(as.character(CDM_SOURCE[1,"recommended_end_date"]), date_format)
#study_start <- as.Date("2020-11-30")


```

## Number of vaccines

This section includes a graph showing the number of vaccine administered by week. 
The data are also shown in the subsequent table. 

```{r plot1, include=TRUE}
t2<-Dataset[N != 0 & !is.na(N), sum(N), by= week]
setnames(t2, "V1", "N")


 p2 <- ggplot(t2, aes(week, N)) +   
         geom_col( alpha = 0.9, fill ="salmon", na.rm=TRUE)+
         scale_x_date(limit= c(monday_start_covid, study_end))

p2
knitr::kable(t2)
```

## Number of vaccines by manufacturer

This section includes a graph showing the number of vaccine administered by week, divided by manifacturer. 
The data are also shown in the subsequent table. 

```{r plot2, include=TRUE}
t1<-Dataset[N != 0 & !is.na(N), sum(N), by= .(week, vx_manufacturer)]
setnames(t1, "V1", "N")
p1<-  ggplot(t1, aes(week, N, fill=vx_manufacturer)) +   
       geom_col(position =position_dodge(preserve = "single"), alpha = 0.9, na.rm=TRUE)+
       scale_x_date(limit= c(monday_start_covid, study_end))

p1

knitr::kable(t1)
```


## Number of vaccines by dose

This section includes a graph showing the number of vaccine administered by week, divided by dose number. 
The data are also shown in the subsequent table.

```{r plot4, include=TRUE}

t4<-Dataset[N != 0 & !is.na(N), sum(N), by= .(week, dose)]

setnames(t4, "V1", "N")

 p4 <- ggplot(t4, aes(week, N)) +   
        geom_col(alpha = 0.9, fill ="salmon", na.rm=TRUE)+
        scale_x_date(limit= c(monday_start_covid, study_end))+
        facet_grid(rows = vars(dose))

p4

knitr::kable(t4)

```

## Number of vaccines by dose and by manufacturer

This section includes a graph showing the number of vaccine administered by week, divided by manifacturer and by dose number. 
The data are also shown in the subsequent table.

```{r plot3, include=TRUE}
 
t3<-Dataset[N != 0 & !is.na(N), sum(N), by= .(week, vx_manufacturer, dose)]

setnames(t3, "V1", "N")

 p3 <- ggplot(t3, aes(week, N, fill=vx_manufacturer)) +   
         geom_col(position = position_dodge(preserve = "single"), alpha = 0.9, na.rm=TRUE)+
         scale_x_date(limit= c(monday_start_covid, study_end))+
         facet_grid(rows = vars(dose))

p3
knitr::kable(t3)
```

```{r include = FALSE}
rm(p1, p2, p3, p4, t1, t2, t3, t4, Dataset)

```