---
title: "FlowChart Description"
output: 
  html_document:
    theme: united
    toc: TRUE
    toc_float: TRUE
params:
  FlowChart: NULL
  ExclusionTable: NULL
---

This is a description of the Flow Chart.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r library, include=FALSE}
if (!require("ggplot2")) install.packages("ggplot2") 
library(ggplot2)
if (!require("data.table")) install.packages("data.table")
library(data.table)
```

```{r Reshaping for Plot, include=FALSE}
  FlowChart = params$FlowChart
  FlowChart<-data.frame(FlowChart)

  n_criteria<-dim(FlowChart)[2]-2
  nrow<-dim(FlowChart)[1]
  criteria<-names(FlowChart)[2:(n_criteria+1)]
  
  for(i in criteria){
    for(j in seq(1, nrow)){
      FlowChart[j, i]=FlowChart[j, i]-2
    }
  }
  
  FlowChart$Included=-3

  for(i in seq(1, nrow)){
    row=FlowChart[i, ][2:(n_criteria+1)]
    criteria_position<-(n_criteria+2) - length(row[row==-2])
    if(length(row[row==-2]) == 0){
      FlowChart[i, "Included" ]=FlowChart[i, "N"] 
    }else{
      FlowChart[i, criteria_position ] = FlowChart[i, "N"]
    }
  }
  
  
  FlowChart<-data.table(FlowChart)
  FlowChart_reshaped<-melt(FlowChart, measure.vars = c(criteria, "Included") )
  FlowChart_reshaped_plot<-FlowChart_reshaped[value>=0,][,-"value"]
```

## Exclusion criteria graph

The next graph shows the proportion of people included in the study and the proportion of people excluded. 
Different colors correspond to different exclusion criteria. 
<br>
```{r  Plot, include=TRUE}
  ggplot(FlowChart_reshaped_plot, aes(monday_week, N, fill=variable))+
    geom_col(position="fill")+
    scale_y_continuous(labels = scales::percent_format())
```


```{r Reshaping for Table, include=FALSE}
  FlowChart_reshaped_table<- dcast(FlowChart_reshaped_plot, monday_week~variable, value.var = "N" )

  FlowChart_reshaped_table <- data.frame(FlowChart_reshaped_table)
  FlowChart_reshaped_table[is.na(FlowChart_reshaped_table)] <- 0

```


## Exclusion criteria table

In the next table each column represents an exclusion criteria and each row represents a week. 
The values in the table refer to the number of persons excluded by the corresponding criteria in that week.
<br>
```{r  Table, include=TRUE}
  paged_table(as.data.frame(FlowChart_reshaped_table))
```

